---
title: "Lab 03 - Nobel laureates"
author: "Marq Schieber"
date: "2/14"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1


```{r number of rows and collumns code}
count(nobel)

ncol(nobel)
```


There are 935 observations and 26 variables. Each row represents one observation.

There are some observations in this dataset that we will exclude from our analysis to match the Buzzfeed results.

### Exercise 2

```{r filter and new data set}
new_nobel <- nobel %>%
filter(country!='NA',
       gender!='org',
       is.na(died_date))
```

WHoops called the new data frame new_nobel.

### Exercise 3
```{r}
new_nobel <- new_nobel %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
```


```{r}
nobel_living_science <- new_nobel %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```


### Exercise 4

Create a faceted bar plot visualizing the relationship between the category of prize and whether the laureate was in the US when they won the nobel prize. Interpret your visualization, and say a few words about whether the Buzzfeed headline is supported by the data.

Your visualization should be faceted by category.
For each facet you should have two bars, one for winners in the US and one for Other.
Flip the coordinates so the bars are horizontal, not vertical.

```{r}
ggplot(data = nobel_living_science, aes(y = country_us)) +
  geom_bar() +
  facet_wrap(~ category)
```

Maybe I'm misunderstanding, but I don't see how this visualization relates to the buzzfeed article. This graph shows US winners vs. outside foreign winners. The buzzfeed article was focused on solely US winners, albeit those who were born in the US and those who immigrated here. 

With that said, this article shows that a significant amount of intellectual talent can be found outside of the United States. This adds support to the article's assertion that the US has much to gain (above what it's already gained) from importing researchers.

...

### Exercise 5

...

### Exercise 6

...
