---
title: "Lab 03 - Nobel laureates"
author: "Marq Schieber"
date: "2/14"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1


```{r number of rows and collumns code}
count(nobel)

ncol(nobel)
```


There are 935 observations and 26 variables. Each row represents one observation.

There are some observations in this dataset that we will exclude from our analysis to match the Buzzfeed results.

### Exercise 2

```{r filter and new data set}
new_nobel <- nobel %>%
filter(country!='NA',
       gender!='org',
       is.na(died_date))
```

WHoops called the new data frame new_nobel.

### Exercise 3
```{r}
new_nobel <- new_nobel %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
```


```{r}
nobel_living_science <- new_nobel %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```


### Exercise 4

```{r}
ggplot(data = nobel_living_science, aes(y = country_us)) +
  geom_bar() +
  facet_wrap(~ category)
```

Maybe I'm misunderstanding, but I don't see how this visualization relates to the buzzfeed article. This graph shows US winners vs. outside foreign winners. The buzzfeed article was focused on solely US winners, albeit those who were born in the US and those who immigrated here. 

With that said, this article shows that a significant amount of intellectual talent can be found outside of the United States. This adds support to the article's assertion that the US has much to gain (above what it's already gained) from importing researchers.

...

### Exercise 5

```{r new variable}
nobel_living_science <- nobel_living_science %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  )

nrow(filter(nobel_living_science, born_country_us == 'USA'))
```

105 winners born in the US.

```{r new bar chart}
ggplot(data = nobel_living_science, aes(y = country_us, fill = born_country_us)) +
  geom_bar() +
  facet_wrap(~ category)
```

The visualization shows that a large proportion of US nobel laureates were born outside the United States. This suggests that immigration is an important part of past US laureates and undoubtedbly future laureates.


...

### Exercise 6

Germany and the UK are tied for most common.

```{r}
filtered_nobel <- nobel_living_science %>%
filter(born_country_us=='Other',
       country_us=='USA')


arrange(count(filtered_nobel, born_country),desc(n))





```


...
